### 2012-09-29 doc/prelim/document/chapters/introduction/introduction.tex
intro updates

\chapter{Introduction}
\label{ch:introduction}
In many fields of engineering and physics, linear and nonlinear
problems are a primary focus of study. Recent focus on multiple
physics systems in the nuclear reactor modeling and simulation
community adds a new level of complexity to common nonlinear systems
as solution strategies change when they are coupled to other problems
\citep{u.s._depertment_of_energy_casl:_2011}. Furthermore, a desire
for predictive simulations to enhance the safety and performance of
nuclear systems creates a need for extremely high fidelity
computations to be performed for these coupled systems as a means to
capture effects not modeled by coarser methods
\citep{keyes_prospects_1997}.

In order to achieve this high fidelity, state-of-the-art computing
facilities must be leveraged in a way that is both efficient and
considerate of hardware-related issues. As scientific computing moves
towards exascale facilities with machines of $O(1,000,000)$ cores
already coming online, new algorithms to solve these complex problems
must be developed to leverage this new hardware
\citep{kogge_using_2011}. Issues such as resiliency to node failure
and scaling to large numbers of cores will be pertinent to robust
algorithms aimed at this new hardware. Considering these issues, this
thesis proposes the development of a massively parallel stochastic
method for linear problems and a novel stochastic method to advance
solution techniques for nonlinear problems.

We discuss in this chapter our motivation developing these Monte Carlo
solvers by providing background on the current state of solver
techniques for multiphysics problems and the hardware that they
leverage. In addition, multiphysics problems of interest to the
nuclear engineering community are provided to further motivate this
work. We then provide a formal presentation of the multiphysics
system and the problems that arise from it.

>>>>

\chapter{Introduction}
\label{ch:introduction}
In many fields of engineering and physics, linear and nonlinear
problems are a primary focus of study. Recent focus on multiple
physics systems in the nuclear reactor modeling and simulation
community adds a new level of complexity to common nonlinear systems
as solution strategies change when they are coupled to other problems
\citep{u.s._department_of_energy_casl:_2011}. Furthermore, a desire
for predictive simulations to enhance the safety and performance of
nuclear systems creates a need for extremely high fidelity
computations to be performed for these coupled systems as a means to
capture effects not modeled by coarser methods.

In order to achieve this high fidelity, state-of-the-art computing
facilities must be leveraged in a way that is both efficient and
considerate of hardware-related issues. As scientific computing moves
towards exascale facilities with machines of $O(1,000,000)$ cores
already coming online, new algorithms to solve these complex problems
must be developed to leverage this new hardware
\citep{kogge_using_2011}. Issues such as resiliency to node failure,
limited growth of memory available per node, and scaling to large
numbers of cores will be pertinent to robust algorithms aimed at this
new hardware. Considering these issues, this preliminary report
proposes the development of a massively parallel stochastic method for
linear problems and a novel stochastic method to advance solution
techniques for nonlinear problems.

We discuss in this chapter our motivation for developing these Monte
Carlo solvers by providing background on the current state of solver
techniques for multiphysics problems and the hardware that they
leverage. In addition, multiphysics problems of interest to the
nuclear engineering community are provided to further motivate this
work. We then provide a formal presentation of the multiphysics system
and the problems that arise from it.
